%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Lâm Quang Vinh} \\[7.5pt]
\href{https://github.com/vinhlq2512}{\raisebox{-0.05\height}\faGithub\ vinhlq2512} \ $|$ \ 
\href{https://www.linkedin.com/in/lqvinh2512/}{\raisebox{-0.05\height}\faLinkedin\ vinhlq2512} \ $|$ \ 
\href{https://lqvinh.dev}{\raisebox{-0.05\height}\faGlobe \ lqvinh.dev} \ $|$ \ 
\href{mailto:vinhlq2512@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ vinhlq2512@gmail.com} \ $|$ \ 
\href{tel:+84 775122001}{\raisebox{-0.05\height}\faMobile \ +84 775122001} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	ABOUT ME / PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\section{Professional Summary}
Full-Stack Developer with over \textbf{4 years of experience} specializing in the .NET ecosystem and modern frontend frameworks. I excel at \textbf{writing clean, maintainable code} using Design Patterns (CQRS, DDD) and \textbf{optimizing database performance} for high-traffic applications. Passionate about technical precision, I have successfully led small teams to deliver stable ERP solutions and complex API integrations. I am a continuous learner who enjoys \textbf{researching and applying new technologies} to enhance system efficiency and deliver innovative software solutions.

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\textbf{Backend Development} \\
.NET Core, ASP.NET Web API, C\#, Entity Framework Core, Dapper, \textbf{Clean Architecture}, \textbf{CQRS}, DDD Pattern. \\[3pt]

\textbf{Database \& Optimization} \\
\textbf{SQL Server (Strong)}, MySQL, Stored Procedures Optimisation, Deadlock Resolution, Database Indexing \& Tuning, Redis. \\[3pt]

\textbf{Frontend Development} \\
Next.js, Blazor, TypeScript, Redux Toolkit, Tailwind CSS, HTML5/CSS3. \\[3pt]

\textbf{Tools \& Integration} \\
Docker, Nginx, \textbf{Kafka (Implementation)}, Git (CI/CD basics), Postman.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

% --- CMC Global ---
\textbf{Senior Full-Stack Developer} \hfill \textbf{Jan 2025 - Present} \\
\textit{CMC Global} \hfill \textit{Hanoi, Vietnam} \\
\textit{Project: Benefit Management}
\begin{itemize}
    \item Developed robust backend services using \textbf{.NET 8} and \textbf{Blazor}, focusing on code quality and component reusability.
    \item \textbf{Performance Tuning:} Analyzed and optimized slow-running SQL queries and implemented Redis caching, resulting in a \textbf{30\% improvement} in API response times.
    \item Collaborated with cross-functional teams to integrate AWS cloud services and payment gateways, ensuring high reliability.
\end{itemize}

\vspace{5pt}

% --- HOPLONG TECH ---
\textbf{Full-Stack Developer \& Team Lead} \hfill \textbf{Jan 2022 - Dec 2024} \\
\textit{HOPLONG TECH} \hfill \textit{Hanoi, Vietnam} \\
\textit{Projects: ERP System \& E-commerce Integration}
\begin{itemize}
    \item \textbf{Technical Leadership:} Led a 4-member team, establishing coding standards using \textbf{Clean Architecture} and \textbf{Fluent Validation} to reduce bugs and technical debt.
    \item \textbf{Integration Specialist:} Independently built a connector system that integrates the Shopee / Lazada / TikTok APIs. Implemented \textbf{Kafka Consumers/Producers} with the Outbox Pattern to ensure data consistency across systems.
    \item \textbf{Database Optimization:} Handled complex data scenarios involving large tables. Successfully resolved critical database \textbf{deadlocks} and optimized Stored Procedures, significantly reducing report generation time.
    \item \textbf{Frontend Implementation:} Developed responsive dashboards using Next.js and Redux, working closely with designers to ensure pixel-perfect implementation.
    \item \textbf{Deployment:} Managed application deployment on Linux servers using Docker and Nginx, ensuring smooth release cycles.
\end{itemize}

\textit{Project: Human Resource Management System (HRMS)}
\begin{itemize}
    \item Developed a comprehensive HR solution using \textbf{.NET Core} following \textbf{Clean Architecture} and \textbf{DDD} principles to manage complex employee lifecycles and contracts.
    \item \textbf{Automated Payroll Engine:} designed a high-performance payroll calculation module using \textbf{Dapper} and Optimized \textbf{Stored Procedures}. Successfully handled complex formulas (tax, insurance, allowances), reducing monthly payroll processing time by \textbf{60\%}.
    \item \textbf{Attendance Tracking:} Built an interactive attendance dashboard with \textbf{Next.js} and \textbf{Redux Toolkit}, handling real-time data synchronization from biometric devices.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Featured Projects}

\textbf{Base Structure (Backend Template)} \hfill \textit{Open Source} \\
\textit{Role: Developer}
\begin{itemize}
    \item Created a standardized .NET backend boilerplate incorporating \textbf{CQRS, MediatR, and DDD} principles.
    \item Purpose: To demonstrate best practices in structuring complex applications and ensuring code maintainability.
\end{itemize}

\vspace{3pt}

\textbf{LETOS (E-commerce)} \hfill \textit{letossafety.vn} \\
\textit{Role: Full-Stack Developer}
\begin{itemize}
    \item Built a product management system with real-time inventory syncing across multiple channels.
    \item Focused on SEO optimization and efficient database schema design.
\end{itemize}


\vfill
\center{\footnotesize Last updated: \today}

\end{document}
